---
title: "qPCR LOD calculation notebook"
output: html_notebook
---

In this notebook, we perform logistic regression on qPCR data.  Data is provided as copy number of template, Ct value, and detected/not-detected (coded as 1 vs. 0).  The LOD in qPCR is typically defined by the copy number that results in detection 95% of the time.  However, since we only have 6 replicate data points at each copy number, we will fit a logistic regression model to the data, and use the model to estimate the LOD.

First, we read in the data from the csv file, "pcr_raw_data.csv":

```{r}
df <- read.csv("pcr_raw_data.csv", header=TRUE)
dim(df)
```

```{r}
head(df)
```

```{r}
names(df)
```

```{r}
attach(df)
```
Next, we fit the logistic regression model:
```{r}
glm.fit=glm(detected~copies, family=binomial, data=df)
summary(glm.fit)
coef(glm.fit)
```
Finally, we plot the data, along with a reference line at p(detected)=0.95:
```{r}
plot(detected~copies, data=df, col="red4")
newdat <- data.frame(copies=seq(min(df$copies), max(df$copies),len=100))
newdat$detected = predict(glm.fit, newdata=newdat, type="response")
lines(detected ~ copies, newdat, col="green4", lwd=2)
abline(h=0.95, col="red")
```
Finally, we calculate the copies using the dose.p function from the MASS library:
```{r}
library(MASS)
dose.p(glm.fit, p=0.95)
```
